%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

    
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Alejandro Gutiérrez Grimaldo} \\ \vspace{1pt}
 
  \small +52 55 1401 6983  
  \href{https://alexgrim.me/}{\underline{alexgrim.me}}
  \href{mailto:alejandro\_grimaldo\_12@outlook.com}{\underline{alejandro\_grimaldo\_12@outlook.com}} 
  \href{https://www.linkedin.com/in/alejandrogrimaldo}{\underline{linkedin.com/in/alejandrogrimaldo}} 
  \href{https://github.com/AlexGrim12}{\underline{github.com/AlexGrim12}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Computer Engineering}{2022 -- Graduating 2027}
{Engineering School -- National Autonomous University of Mexico (UNAM)}{Mexico City, Mexico}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Competitor \& Software Engineer}{February 2023 -- Present}
{Competitive Programming Club (CPCFI)}{Engineering School, UNAM}
\resumeItemListStart
\resumeItem{Participated in the {\textbf{ICPC Mexico 2023}} (top 20\%)  and {\textbf{IEEEXtreme 17.0}} (top 15 Mx), solving algorithmic problems using {\textbf{C++}} and {\textbf{Python}}.}
\resumeItem{Co-developed a web application that improved competitor management by 30\% and integrated an \textbf{online compiler} to streamline workflows. }
\resumeItem{Designed and developed a scalable web application using TypeScript, React, NextJS, PostgreSQL, Tailwind, and Docker, enhancing competitor collaboration. {$ | $} {\href{http://www.cpcfi.unam.mx:3000} {\underline{cpcfi.unam.mx}}}}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{August 2024 -- Present}
{IEEE Computer Society}{Engineering School, UNAM}
\resumeItemListStart
\resumeItem{Developed a {\textbf{chatbot to guide 500+ new engineering students}} through orientation, utilizing Python and AI-based frameworks to automate responses and improve user experience.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------HACKATHONS & COMPETITIONS-----------
\section{Awards}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{HackMonterrey - Capital One Challenge}  {$ | $} {\href{https://asterionconnect.vercel.app/} {\underline{asterionconnect.vercel.app}}}}{September 2024}
\resumeItemListStart
\resumeItem{Secured \textbf{4th place} out of 20+ teams by developing a \textbf{social network for achieving financial goals}.}
\resumeItem{Designed and implemented a interface that allowed users to \textbf{set and track financial goals}, share progress, and receive personalized recommendations. Used AI to analyze user entrepreneur projects.}
\resumeItem{\textit{Technologies used:} TypeScript, React, Tailwind, NextJS, Python, Flask, Firebase (Firestore DB, Storage, Authentication).}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Hackthion - Notion Hackathon}  {$ | $} {\href{https://study-brown.vercel.app//} {\underline{study-brown.vercel.app}}}}{July 2024}
\resumeItemListStart
\resumeItem{Achieved \textbf{2nd place} out of 20+ teams by developing a \textbf{social network for students} to share Notion notes. }
\resumeItem{Conceptualized, developed, and presented a prototype to an audience and a jury, effectively demonstrating its functionality and potential to promote adoption.}
\resumeItem{\textit{Technologies used:} TypeScript, React, Tailwind, NextJS, Python, Flask, PostgreSQL.}
\resumeItemListEnd

% \resumeSubheading
% {AI Lab School Hackathon}{May 2024}
% {AI Lab School -- Iollin}{Online Hackathon}
% \resumeItemListStart
% \resumeItem{{\textbf{1st place}} among +10 teams, developed an enterprise assistant application using {\textbf{NextJS}} and {\textbf{OpenAI API}}.}
% \resumeItemListEnd

\resumeProjectHeading
{\textbf{AI Lab School Hackathon} {$ | $} {\href{https://ai-hackathon-webapp.vercel.app/} {\underline{ai-hackathon-webapp.vercel.app}}}}{May 2024}
\resumeItemListStart
\resumeItem{Won \textbf{1st place} out of 10+ teams by creating a \textbf{generative AI-powered business assistant} that analyzed market data and optimized social media strategies.}
\resumeItem{\textit{Technologies used:} TypeScript, React, NextJS, Python, OpenAI API.}
\resumeItemListEnd

% \resumeSubheading
% {AngelHack Mexico}{April 2024}
% {AngelHack}{IPN Zacatenco, CDMX}
% \resumeItemListStart
% \resumeItem{{\textbf{2nd place}} in the social responsibility track among +50 teams, developed a food marketplace application using {\textbf{NextJS}} and {\textbf{OpenAI API}}.}
% \resumeItemListEnd

\resumeProjectHeading
{\textbf{AngelHack - Mexico \& Global} {$ | $} {\href{https://hack-mexico.vercel.app/landingpage} {\underline{hack-mexico.vercel.app}}}}{April 2024}
\resumeItemListStart
\resumeItem{Secured \textbf{2nd place} out of 50+ teams for developing a \textbf{food marketplace} that used AI-driven image recognition to reduce food waste and optimize food sales.}
% Obtuvo el quito lugar mundial lo que le permitio clasificar a la final mundial de en singapur. 
\resumeItem{Secured a spot in the \textbf{global finals in Singapore} by ranking \textbf{5th worldwide}.}
\resumeItem{\textit{Technologies used:} TypeScript, React, NextJS, OpenAI API.}
\resumeItemListEnd

% \resumeSubheading
% {Anticorruption Dataton}{December 2023}
% {SESNA -- (Secretariat of the National Anticorruption System) }{Online Hackathon}
% \resumeItemListStart
% \resumeItem{{\textbf{4th place}}, developed a user-friendly interface for algorithmic result visualization using {\textbf{Django}} and {\textbf{React}}.}
% \resumeItemListEnd

% \resumeSubheading
% {International Space Apps Challenge}{October 2023}
% {NASA -- AEF (Mexican Space Administration)}{Intercontinental University, CDMX}
% \resumeItemListStart
% \resumeItem{{\textbf{Led a team}} to develop a mobile application using {\textbf{Flutter}}, creating a {\textbf{chatbot}} with {\textbf{Google's LLM Palm2}}.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------COURSES & CERTIFICATIONS-----------
\section{Courses}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Cisco Network Technician Career Path}}{January -- April 2024}
\resumeItemListStart
\resumeItem{Completed the path, gaining hands-on experience in \textbf{designing} and \textbf{managing secure networks} with a focus on routing and switching protocols.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Google Cloud Computing Foundations}}{September -- October 2023}
\resumeItemListStart
\resumeItem{Acquired skills in deploying secure cloud solutions on \textbf{Google Cloud Platform} with a focus on \textbf{Compute Engine} and \textbf{Networking}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Focus} $|$ To-do Mobile App}{June 2024}
\resumeItemListStart
\resumeItem{Developed a mobile application for task management and productivity improvement, using {\textbf{Flutter}} and {\textbf{Google Firebase}}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Game of life} $|$ Mobile Game}{October 2023}
\resumeItemListStart
\resumeItem{Developed a mobile game using {\textbf{Flutter}}, implementing the {\textbf{Conway's Game of Life}} algorithm.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: English (Proficient), Spanish (Native Speaker)} \\
        \textbf{Programming Languages}{: C/C++, Python, Java, JavaScript/TypeScript, Dart} \\
        % \textbf{Frameworks}{: React, NextJS, Express, Flutter} \\
        \textbf{Developer Tools}{: Git/GitHub, Google Cloud Platform, Microsoft Azure} \\
        }}
\end{itemize}

\end{document}
